### 2014-11-12 tex/intro.tex
changes to intro

Research in the abstract interpretation community has taken
a very different approach to analyzing heap manipulating
programs which computes a summary of possible heaps. 
These techniques start with an initial heap configuration 
and then using a static analysis, make updates to the
heap following program semantics, ultimately creating a heap 
summary which represents the potential heaps resulting from
program execution~\cite{Dillig:2011}. Because these
techniques are based on a static analysis, the heap summaries
over-approximate the set of feasible heap configurations.
%The primary challenge relative to heap
%analysis for these techniques is to 
%resolve potential dependencies of local results on the global
%aliases in the heap. 
%Recent work addresses these issues
%through strong updates to heap locations 
%at call sites~\cite{Dillig} and computation of dangerous 
%aliases~\cite{Matosevic}. Because these techniques are based 
%on a static analysis, the resulting summaries over-approximate
%the actual potential heaps.

>>>>

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. To achieve
this goal, we found inspiration from recent work in the domain of
static analysis that uses sets of constraints over heap locations to
encode multiple heaps in a single representation. These sets,
sometimes known as value sets or value summaries, allow multiple heaps
to be represented simultaneously with a higher degree of precision
than afforded by traditional shape analysis techniques. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{..}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{..}. For these reasons the techniques use
over-approximations to reason about heaps and may report false
positives. Also, an update to the heap required a rewrite of the
constraint system making it prohitive for use in the context of
symbolic execution.

%The goal of this work is find a more compact representation of the heaps
%and be better able to leverage constraint solvers.
%The  But any update of the heap required a rewrite on the constraint system
%or simply was not opssible to initialize and handle the aliasing possiblities.

%The goal is to leverage that

%Research in the abstract interpretation community has taken a very
%different approach to analyzing heap manipulating programs which
%computes a summary of possible heaps.  These techniques start with an
%initial heap configuration and then using a static analysis, make
%updates to the heap following program semantics, ultimately creating
%a heap summary which represents the potential heaps resulting from
%program execution~\cite{Dillig:2011}. Because these techniques are
%based on a static analysis, the heap summaries over-approximate the
%set of feasible heap configurations.

%The primary challenge relative to heap analysis for these techniques
%is to resolve potential dependencies of local results on the global
%aliases in the heap.  Recent work addresses these issues through
%strong updates to heap locations at call sites~\cite{Dillig} and
%computation of dangerous aliases~\cite{Matosevic}. Because these
%techniques are based on a static analysis, the resulting summaries
%over-approximate the actual potential heaps.
